---
title: "MarkDown_003"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

To start, let’s look at bolding and italicising text. To bold text, you surround it by two asterisks on either side. Similarly, to italicise text, you surround the word with a single asterisk on either side. **bold** and *italics* respectively.

We’ve also seen from the default document that you can make section headers. To do this, you put a series of hash marks (#). The number of hash marks determines what level of heading it is. One hash is the highest level and will make the largest text (see the first line of this lecture), two hashes is the next highest level and so on. Play around with this formatting and make a series of headers, like so:

# Header level 1
## Header level 2
### Header level 3...

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
